\chapter{Ethics and Security}
\label{cha:ethics}
\instructions{
\textit{This section is not covered by the page limit.}
}

\section{Ethics}
\label{sec:ethics}
\instructions{
If you have entered any ethics issues in the ethical issue table in the administrative proposal forms, you must:
\begin{itemize}
\item submit an ethics self-assessment, which:
\begin{itemize}
\item describes how the proposal meets the national legal and ethical requirements of the country or countries where the tasks raising ethical issues are to be carried out; 
\item explains in detail how you intend to address the issues in the ethical issues table, in particular as regard:
\begin{itemize}
\item research objectives (e.g. study of vulnerable populations, dual use, etc.)
\item research methodology (e.g. clinical trials, involvement of children and related consent procedures, protection of any data collected, etc.) 
\item the potential impact of the research (e.g. dual use issues, environmental damage, stigmatisation of particular social groups, political or financial retaliation, benefit-sharing, misuse, etc.).
\end{itemize}
\end{itemize}
\item provide the documents that you need under national law(if you already have them), e.g.:
\begin{itemize}
\item an ethics committee opinion;
\item the document notifying activities raising ethical issues or authorising such activities;
\end{itemize}
\end{itemize}
\textit{\indent If these documents are not in English, you must also submit an English summary of them (containing, if available, the conclusions of the committee or authority concerned).}
\vskip0.2cm
\textit{If you plan to request these documents specifically for the project you are proposing, your request must contain an explicit reference to the project title.}
}

{\acro} is a project devoted to research and development that will lead to data products and tools to apply selection functions to the analysis of data collected by a space astrophysics mission and other surveys. Hence, no ethics issues are expected to arise in the project. This is indicated in the form filled out online in the Funding \& tender opportunities portal. Specific clarifications:
\begin{itemize}
    \item Research and development in {\acro} is conducted on publicly available data from astronomical surveys. We will also make use of information from the Gaia Data Processing and Analysis Consortium (DPAC) to which the coordinator and several participants have access (as members of DPAC). For the participants who are not members of DPAC but need access to its non-public information, a standard non-disclosure agreement (NDA) already exists which the participants in question will sign. In particular we stress:
    \begin{itemize}
        \item the research, development, and implementation of tools proposed here do not involve human participants, human tissue, human embryos/foetuses, cells, or animals.
        \item no personal data is collected or processed for the purpose of the effort proposed.
    \end{itemize}
    \item Two third countries are involved, Australia and the United States of America.
    \begin{itemize}
        \item They will participate in the {\acro} research, development, and implementation of tools. As such they will be working with the publicly available data mentioned above and any source code written by these partners (as part of the {\acro} effort) will become part of the {\acro} tools that will be made publicly available.
        \item No personal data will be imported from or exported to the non-EU partners.
        \item No activities will be undertaken by the non-EU partners that are prohibited in the EU.
        \item Any data exchange with the non-EU partners will only involve publicly available data to which the non-EU partners have access. In case DPAC information needs to be exchanged the NDA referred to above will also be applied to the non-EU partners.
    \end{itemize}
    \item The purpose of {\acro} is to advance astronomical research by enabling a much more advanced use of Gaia and other survey data than is possible today. Hence the focus of the efforts proposed here is exclusively civilian.
\end{itemize}

\section{Security}
\label{sec:security}
\begin{itemize}
\item Activities or results raising security issues: NO
\item `EU-classified information' as background or results: NO
\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proposal-main"
%%% End: